Generalized Plackett-Luce Likelihoods

### 2022-08-10 inst/jss_hyper3.Rnw
rewording

Thus the additional support gained in moving from $a=\frac{1}{2}$ to
the evaluate of $a=\sqrt{2}-1$ is 0.029, rather small [as might be
expected given that we have only one rather uninformative observation,
and also given that the maximum likelihood estimate ($\simeq 0.41$) is
quite close to the null of $0.5$].  Nevertheless we can apply Wilks's
theorem for a $p$-value:

@@

The ideas presented above can easily be extended to arbitrarily large
numbers of competitors.  Given an order statistic of the type
considered above, the Mann-Whitney-Wilcoxon
test~\citep{mann1947,wilcoxon1945} assesses a null of identity of
underlying distributions.  Consider the chorioamnion dataset at
\code{wilcox.test.Rd}:

>>>>

Thus the additional support gained in moving from $a=\frac{1}{2}$ to
the evaluate of $a=\sqrt{2}-1$ is 0.029, rather small [as might be
expected given that we have only one rather uninformative observation,
and also given that the maximum likelihood estimate ($\simeq 0.41$) is
quite close to the null of $0.5$].  Nevertheless we can follow
\cite{edwards1972} and apply Wilks's theorem for a $p$-value:

@@

The ideas presented above can easily be extended to arbitrarily large
numbers of competitors, although the analytical expressions tend to be
intractable and numerical methods must be used.  Given an order
statistic of the type considered above, the Mann-Whitney-Wilcoxon
test~\citep{mann1947,wilcoxon1945} assesses a null of identity of
underlying distributions.  Consider the chorioamnion dataset at
\code{wilcox.test.Rd}:
